\LARGE The Bitcoin Lightning Network:\\ \Large Scalable Off-Chain Instant Payments

### 2015-10-22 paper.tex
Thanks to @jlopp (Jameson Lopp) for the corrections

Changes are necessary to bitcoin, such as the malleability soft-fork.
Additionally, if this system becomes popular, it will be necessary for the
system to securely transact with many users and some kind of structure like a
blockheigh timestop will be desirable. This system assumes such changes to
enable Lightning Network to exist entirely, as well as soft-forks ensuring the
security is robust against attackers will occur. While the system may continue
to operate with only some time lock and malleability soft-forks, there will be
necessary soft-forks regarding systemic risks. Without proper community
foresight, an inability to establish a timestop or similar function will allow
systemic attacks to take place and may not be recognized as imperative until an
attack actually occurs.

@@

If all transaction using Bitcoin were conducted inside a network of micropayment
channels, to enable 7 billion people to make two channels per year with
unlimited transactions inside the channel, it would require 133 MB blocks
(presuming 500 bytes per transaction and 52560 blocks per year). Current
generation desktop computers will be able to run a full node with old blocks
pruned out on 2TB of storage.

>>>>

Changes are necessary to bitcoin, such as the malleability soft-fork.
Additionally, if this system becomes popular, it will be necessary for the
system to securely transact with many users and some kind of structure like a
blockheight timestop will be desirable. This system assumes such changes to
enable Lightning Network to exist entirely, as well as soft-forks ensuring the
security is robust against attackers will occur. While the system may continue
to operate with only some time lock and malleability soft-forks, there will be
necessary soft-forks regarding systemic risks. Without proper community
foresight, an inability to establish a timestop or similar function will allow
systemic attacks to take place and may not be recognized as imperative until an
attack actually occurs.

@@

If all transactions using Bitcoin were conducted inside a network of
micropayment channels, to enable 7 billion people to make two channels per year
with unlimited transactions inside the channel, it would require 133 MB blocks
(presuming 500 bytes per transaction and 52560 blocks per year). Current
generation desktop computers will be able to run a full node with old blocks
pruned out on 2TB of storage.
